Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-18 chapters/discussion/discussion.tex
minor change

This thesis proposed a probabilistic model for image geo-calibration.
The key to the success of this model is to find constraint functions
that describe the relationship between geo-calibration parameters and
the image content. We developed constraint functions for different set
of parameters that can fit to the model.  Furthermore, we also show
that learning to geo-calibrate cameras helps learning useful features
for image understanding.  There are several possible future research
directions for extending this work, including: exploiting map data in
cross-view learning, replacing the CNN networks in our algorithms with
Bayesian neural networks (BNNs).  Overall, we hope our work can
provide new ways for geo-calibration and pre-task training.

>>>>

This thesis proposed a flexible probabilistic framework for image
geo-calibration. The key to the success of the framework is to find
constraint functions that can accurately model the relationship between
geo-calibration parameters and the image content. 
We developed constraint functions for different set of parameters to
fit to the framework. 
Furthermore, we also show that learning to geo-calibrate cameras helps
learning useful features for image understanding. There are several
possible future research directions for extending this work,
including: exploiting map data in cross-view learning, replacing the
CNN networks in our algorithms with Bayesian neural networks (BNNs).
Overall, we hope our work can provide new ways for geo-calibration and
pretext task for learning image representations.
